Rust for Scientific Computing

### 2025-09-01 paper/main.tex
formatting
cleanup
example table for crates

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[hidelinks]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsmath,amssymb,amsthm}
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{doi}
\usepackage{acronym}
\usepackage{listings}
\usepackage{tikz}
\usepackage[backend=biber,style=ieee]{biblatex}

@@

\newacro{abm}[ABM]{Agent-Based Model}
\newacro{cabm}[CABM]{Cellular Agent-Based Model}
\newacro{ca}[CA]{Cellular Automaton}
\newacroplural{ca}[CA]{Cellular Automata}

@@

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[hidelinks]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsmath,amssymb,amsthm}
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{doi}
\usepackage{listings}
\usepackage{tikz}
\usepackage[backend=biber,style=ieee]{biblatex}

@@

@@

\begin{table*}
    \centering
    \begin{tabular}{l r r r r r}
        \toprule
        Crate Name &Last Update &Version &$N_d$ &$D_\text{week}$ &$D_\text{total}$\\
        \midrule
        Lamellar         &2025-03-31 &0.7.1      &42   &20       &     16.9k\\
        argmin           &2024-02-27 &0.10.0     &18   &12003    &   1227.7k\\
        arrow            &2025-08-25 &56.1.0     &23   &7532     &  27425.0k\\
        bevy             &2025-05-30 &0.16.1     &35   &10175    &   2847.7k\\
        bless            &2025-07-20 &0.1.1      &13   &80       &      0.6k\\
        burn             &2025-07-18 &0.18.0     &12   &1793     &    319.7k\\
        c3dio            &2024-04-08 &0.8.0      &2    &24       &     11.8k\\
        cargo-upgrades   &2025-08-25 &2.2.4      &10   &553      &     64.7k\\
        cellular\_raza   &2025-08-05 &0.3.0      &10   &157      &     27.4k\\
        cfsem            &2025-08-14 &2.5.0      &8    &106      &      4.9k\\
        city2ba          &2020-02-28 &1.1.0      &20   &19       &      3.0k\\
        cmake            &2025-02-10 &0.1.54     &1    &899615   &  91211.9k\\
        cudarc           &2025-08-07 &0.17.2     &5    &1184     &    647.0k\\
        cxxbridge        &2019-12-28 &0.0.0      &0    &14       &      1.3k\\
        deimos           &2025-06-23 &0.10.0     &13   &40       &      7.1k\\
        diffsol          &2025-07-16 &0.6.6      &16   &131      &     33.9k\\
        dioxus           &2025-08-11 &0.6.3      &28   &         &    637.5k\\
        egobox           &2025-08-22 &0.32.0     &18   &250      &     35.6k\\
        enzyme           &2021-12-26 &0.4.0      &5    &17       &      5.4k\\
        extendr-api      &2025-07-12 &0.8.1      &11   &968      &    178.4k\\
        factrs           &2025-01-13 &0.2.0      &20   &24       &      1.8k\\
        faer             &2025-04-29 &0.22.6     &46   &1322     &    528.4k\\
        faucet           &2025-05-31 &0.2.0      &7    &33       &      3.0k\\
        fem\_2D          &2023-04-20 &0.2.2      &6    &20       &      5.4k\\
        gcv\_spline      &2024-01-28 &0.2.0      &1    &16       &      2.5k\\
        \bottomrule
    \end{tabular}
    \caption{TODO}
\end{table*}
